---
title: "R Notebook"
output: html_notebook
---

```{r, setup, include=FALSE}
# load packages
library(dplyr)
library(tidyverse)
```

We start by loading the dataset to begin our analysis. An convert the column for date to the correct data type. We also clean the dataset by removing any rows that contain null values.

```{r}
shopper_data <- read_csv("2019 Winter Data Science Intern Challenge Data Set - Sheet1.csv")
shopper_data$created_at <- as.POSIXct(shopper_data$created_at, format = "%Y-%m-%d %H:%M:%S")
shopper_data <- na.omit(shopper_data)
head(shopper_data)
```

To gain additional insight, we print certain key values that will give us addional insight on the dataset. 

```{r}
# Print the shape of the datset
dim(shopper_data)

# Determine the range of dates for the dataset
shopper_data %>% 
  mutate(created_date = as.Date(as.character(created_at))) %>%
  summarise(min = min(created_date), max = max(created_date))
  
# Get the AOV and average item cost
round(mean(shopper_data$order_amount), 2)
round(mean(shopper_data$order_amount/shopper_data$total_items), 2)

# Orders over 1000$
big_orders <- shopper_data[shopper_data$order_amount > 1000,]
dim(big_orders)
big_orders
```

From the printed values, we see that the dataset indeed spans a month of time. Furthermore, we obtain similar AOV as presented in the problem description. Upon closer investigation of the dataset, we see that there are a few very large orders that skew the dataset. In fact, most orders are under 1000\$, so we decide to remove all orders above 1000\$ to get a more accurate representation of the order value.

```{r}
# Orders under 1000$
small_orders <- shopper_data[!shopper_data$order_amount > 1000,]
dim(small_orders)
head(small_orders)

# Get the AOV and average item cost
round(mean(small_orders$order_amount), 2)
round(mean(small_orders$order_amount/small_orders$total_items), 2)
```

```{r}
# Get median order value
round(median(shopper_data$order_amount), 2)
```

